\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-29 journalWallFriction/theory2robAlgs.tex
updated pictures

\begin{figure*}
\begin{overpic}[width=0.67\columnwidth]{regionMove1.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove2.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove3.pdf}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{regionMove4.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove5.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove6.pdf}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move1.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move2.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move3.pdf}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each the move 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}
To compute the 2-move reachable set for a circular workspace, first consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the workspace.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

>>>>

\begin{figure*}
\begin{overpic}[width=0.67\columnwidth]{regionMove1.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,  - , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove2.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove3.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{regionMove4.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove5.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove6.pdf}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move1.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move2.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move3.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each the move 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}
To compute the 2-move reachable set for a circular workspace, first consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the workspace.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.
